---
title: "DEN Subgraphs"
output: html_document
date: "2022-08-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```

# DEN Subgraphs for The Ties that Bind: A social network analysis of cultural capital in Denmark
To load data required for subgraphs into R environment, run Projecting DEN.Rmd

# Load Packages

```{r}
library(igraph)
library(igraphdata)
library(scales)
library(dplyr)

library(stargazer)
library(ggplot2)
library(ergm)
library(pals)

library(imputeTS)
library(tidyr)
```

```{r}
#Load data from soc.elite
library(devtools)   
install_github("antongrau/soc.elite", force = TRUE)   

#Load den
data(den) 

#Load pe13
data(pe13)
```

```{r}
#Load data
den_mine <- read.csv("den_mine.csv", header = TRUE) #Output of Projecting DEN.Rmd
gender_df <- read.csv("gender_df.csv", header = TRUE) #Output of Projecting DEN.Rmd
```

# Original Biparitite DEN (den_ntwk)

```{r}
edgelist <- droplevels(data.frame(name = den$NAME, affiliation = den$AFFILIATION))
den_ntwk <- graph_from_edgelist(as.matrix(edgelist), directed = FALSE)
V(den_ntwk)$type <- V(den_ntwk)$name %in% edgelist[,2] #TRUE type are affiliations
```

```{r}
summary(den_ntwk)
```

# Projected DEN (den_mine_ntwk)

```{r}
#Create graph
den_mine_ntwk <- graph_from_edgelist(as.matrix(den_mine[,1:2]), directed = FALSE)

#Edge attributes
E(den_mine_ntwk)$affiliation <- den_mine$affiliation #Affiliation Name
E(den_mine_ntwk)$weight <- den_mine$weight #Weight
E(den_mine_ntwk)$cultural <- den_mine$cultural #Cultural

#Reorder gender_df to match network
gender_df <- gender_df[match(V(den_mine_ntwk)$name, gender_df$name),]

#Vertex Attributes
V(den_mine_ntwk)$gender <- gender_df$gender
V(den_mine_ntwk)$ncc <- gender_df$ncc
V(den_mine_ntwk)$ncc <- round(V(den_mine_ntwk)$ncc, digits = 0) #Get to round numbers
```

```{r}
summary(den_mine_ntwk)
```

# Largest DEN Component (den_mine_largest)

```{r}
# count_components(den_mine_ntwk) #834
# components(den_mine_ntwk)$csize

#Decompose full projected network into components
den_mine_largest <- decompose(den_mine_ntwk, mode = "strong", max.comps = 1)

#Save largest component
den_mine_largest <- den_mine_largest[[1]]
```

```{r}
summary(den_mine_largest)
```


# Core DEN (core_subgraph)
```{r}
#Get names of core members
core_names <- pe13$Name

#Logical vector for whether or not given node is in core
in_core <- V(den_mine_largest)$name %in% core_names

#Creating subgraph
core_subgraph <- induced_subgraph(den_mine_largest, in_core)
```

## Vertex Attributes
```{r}
#Reorder gender_df to match network
pe13 <- pe13[match(V(core_subgraph)$name, pe13$Name),]

#Vertex Attributes
V(core_subgraph)$famclass <- pe13$Family_class
V(core_subgraph)$uni <- pe13$University
V(core_subgraph)$gymnasium <- pe13$Gymnasium
V(core_subgraph)$age <- pe13$Age
V(core_subgraph)$sector <- pe13$Sector
V(core_subgraph)$educat <- pe13$Education_cat
```

```{r}
#Imputing means and filling in data
agemeans<- na_mean(V(core_subgraph)$age)
V(core_subgraph)$age <- agemeans

V(core_subgraph)$uni <- V(core_subgraph)$uni %>% replace_na('MISSING')
V(core_subgraph)$gymnasium <- V(core_subgraph)$gymnasium %>% replace_na('MISSING')
```

```{r}
summary(core_subgraph)
```

# Largest DEN Component — Cultural Split (cultural_graph, not_cultural_graph)

```{r}
#Cultural edges
cultural_edges <- E(den_mine_largest)[E(den_mine_largest)$cultural == 1]
not_cultural_edges <- E(den_mine_largest)[E(den_mine_largest)$cultural == 0]

#Split graph
cultural_graph <- den_mine_largest - not_cultural_edges
not_cultural_graph <- den_mine_largest - cultural_edges
```

```{r}
summary(cultural_graph)
summary(not_cultural_graph)
```

# Core DEN - Cultural Split (culture_core, nonculture_core)

```{r}
#Cultural edges
core_cultural_edges <- E(core_subgraph)[E(core_subgraph)$cultural == 1]
core_not_cultural_edges <- E(core_subgraph)[E(core_subgraph)$cultural == 0]

#Split graph
culture_core <- core_subgraph - core_not_cultural_edges
nonculture_core <- core_subgraph - core_cultural_edges
```

```{r}
summary(culture_core)
summary(nonculture_core)
```

# Exports

```{r}
#Largest Component DEN
write_graph(den_mine_ntwk,
  "den_mine_ntwk.csv",
  format = "edgelist")
  
#Core DEN
write_graph(core_subgraph,
  "core_subgraph.csv",
  format = "edgelist")

#Largest Component DEN — Cultural Split
write_graph(core_subgraph,
  "core_subgraph.csv",
  format = "edgelist")

write_graph(core_subgraph,
  "core_subgraph.csv",
  format = "edgelist")

#Core DEN — Cultural Split
write_graph(core_subgraph,
  "core_subgraph.csv",
  format = "edgelist")

write_graph(core_subgraph,
  "core_subgraph.csv",
  format = "edgelist")
```



