---
title: "RQ1: How is cultural capital distributed in the network of Danish elites?"
output: html_document
date: '2022-06-08'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```


# RQ1: How is cultural capital distributed in the network of Danish elites?
To load network objects required for subsequent analysis into global R environment, run DEN Subgraphs.Rmd

# Load packages 

```{r}
library(igraph)
library(igraphdata)
library(scales)
library(dplyr)

library(stargazer)
library(ggplot2)
library(ergm)
library(pals)
library(e1071)
```


### Projected DEN
```{r}
#Proportion of affiliations that are cultural
table(culture_df$cultural_label)
prop_cultural <- 646/5079
print(prop_cultural) #12.7%

#Distribution in Projected DEN
summary(V(den_mine_ntwk)$ncc)
summary(V(den_mine_largest)$ncc)
table(V(den_mine_ntwk)$ncc) #Mean: 0.1373

# Proportion with any cultural capital
any_ncc <- induced_subgraph(den_mine_ntwk, V(den_mine_ntwk)$ncc > 0)
print(length(V(any_ncc)$name)/length(V(den_mine_ntwk)$name)) #11.9%
```

### Largest Component DEN
```{r}
#Distribution in Largest Component DEN
summary(V(den_mine_largest)$ncc)
table(V(den_mine_largest)$ncc) #Mean: 0.1378

#Individuals with high or any ncc
high_ncc <- induced_subgraph(den_mine_largest, V(den_mine_largest)$ncc > 4)
any_ncc <- induced_subgraph(den_mine_largest, V(den_mine_largest)$ncc > 0)

# Proportion with any cultural capital
print(length(V(any_ncc)$name)/length(V(den_mine_largest)$name)) #11.8%

# Proportion with high cultural capital
print(length(V(high_ncc)$name)/length(V(den_mine_largest)$name)) #0.06%
```

### Core DEN
```{r}
#Distribution in Core DEN
table(V(core_subgraph)$ncc)
core_any_ncc <- induced_subgraph(core_subgraph, V(core_subgraph)$ncc > 0)

# Proportion with any cultural capital
print(length(V(core_any_ncc)$name)/nrow(pe13)) #37.1%
```

### Summary Comparison
```{r}
summary(V(den_mine_ntwk)$ncc)
summary(V(den_mine_largest)$ncc)
summary(V(core_subgraph)$ncc)
```

```{r}
#Variances
var(V(den_mine_ntwk)$ncc)
var(V(den_mine_largest)$ncc)
var(V(core_subgraph)$ncc)
```

# Degree in Original Bipartite DEN

```{r}
#Degrees from Original Bipartite DEN
types <- V(den_ntwk)$type #Separate nodes into individual- and affiliation-type
deg <- degree(den_ntwk) #Calculate degrees

#Dataframe
degree_df <- data.frame(names = V(den_ntwk)$name, types, deg)
degree_df <- degree_df[degree_df$types == FALSE,] #Take only individual-type nodes
```

```{r}
#Plotting degrees
summary(degree_df$deg)
hist(degree_df$deg)

#Degrees in core
degree_df_core <- degree_df[in_core,]
summary(degree_df_core$deg)
hist(degree_df_core$deg)
```

```{r}
#Plots of degrees
#Title: Degree of Individual-Type Nodes
require(gridExtra)
require(grid)

hist_full<-ggplot(degree_df, aes(x=deg)) + 
  geom_histogram(color="black", fill="white",
                 binwidth = 1) +
  geom_vline(aes(xintercept=mean(deg)),
            color="lightblue", linetype="dashed", size=1) +
  ggtitle("Full DEN") +
  xlab("Degree") +
  ylab("Nodes")


hist_core<-ggplot(degree_df_core, aes(x=deg)) + 
  geom_histogram(color="black", fill="white",
                 binwidth = 1) + 
  geom_vline(aes(xintercept=mean(deg)),
            color="lightblue", linetype="dashed", size=1) +
  ggtitle("Core Members") +
  xlab("Degree") +
  ylab("Nodes") 


grid.arrange(hist_full, hist_core, ncol=2)
```

```{r}
# Install & load scales
library("scales")

#Plots of NCC
ncc_df <- data.frame(name = V(den_mine_ntwk)$name, ncc = V(den_mine_ntwk)$ncc)
ncc_df_core <- ncc_df[V(den_mine_ntwk)$name %in% core_names,]

hist_ncc_full<-ggplot(ncc_df, aes(x=ncc)) + 
  geom_histogram(color="black", fill="white",
                 binwidth = 1) +
  geom_vline(aes(xintercept=mean(ncc)),
            color="lightblue", linetype="dashed", size=1) +
  ggtitle("Full DEN") +
  xlab("NCC") +
  ylab("Nodes") +
  scale_x_continuous(breaks = pretty_breaks())


hist_ncc_core<-ggplot(ncc_df_core, aes(x=ncc)) + 
  geom_histogram(color="black", fill="white",
                 binwidth = 1) + 
  geom_vline(aes(xintercept=mean(ncc)),
            color="lightblue", linetype="dashed", size=1) +
  ggtitle("Core Members") +
  xlab("NCC") +
  ylab("Nodes") +
  scale_x_continuous(breaks = pretty_breaks())


grid.arrange(hist_ncc_full, hist_ncc_core, ncol=2)
```

```{r}
#Comparison with NCC
skewness(degree_df$deg)
skewness(V(den_mine_largest)$ncc)
skewness(V(den_mine_ntwk)$ncc)
```


```{r}
#Degree distribution and CCDF

# Get the distribution of ncc
ncc_prob <- rep(0,9)
for (i in 1:length(V(den_mine_largest)$ncc)){
  ncc_prob[V(den_mine_largest)$ncc[i] + 1] <- ncc_prob[V(den_mine_largest)$ncc[i] + 1] + 1
}


ncc_prob <- ncc_prob/length(V(den_mine_largest)$ncc) #THIS IS THE ISSUE
print(ncc_prob)

# Remove degree=0
ncc_prob <- ncc_prob[-1] 

# Remove degrees with proportion=0
nonzero_pos <- which(ncc_prob!=0)
ncc_prob <- ncc_prob[nonzero_pos]

# Create a vector including all non-zero-probability degrees
degr <- 1:max(V(den_mine_largest)$ncc)
degr <- degr[nonzero_pos]

#CCDF Calculate
ncc_ccdf <- NULL
for (i in 1:length(ncc_prob)) {
  ncc_ccdf[i] = sum( ncc_prob[ seq(i, length(ncc_prob)) ] )
}

#CCDF Plot
plot(ncc_ccdf ~ degr, xlab='NCC i', ylab='Complementary CDF P(X>=i)', log='xy', col='blue')

```

```{r}
library(patchwork)

ncc_df <- data.frame(ncc_prob, degr)
ncc_cc_df <- data.frame(ncc_ccdf, degr)

nccprob <- ggplot(ncc_df, aes(x = degr, y = ncc_prob)) + geom_point()
nccprob <- nccprob + labs(x = "NCC", y = "Probability P(X=i)", title = "NCC Probability Distribution")
nccprob <- nccprob + theme(plot.title = element_text(hjust = 0.5)) 

ccdf <- ggplot(ncc_cc_df, aes(x = degr, y = ncc_ccdf)) + geom_point() 
ccdf <- ccdf + scale_x_continuous(trans='log10') + scale_y_continuous(trans='log10')
ccdf <- ccdf + labs(x = "NCC", y = "Complementary CDF P(X>=i)", title = "NCC CCDF") 
ccdf <- ccdf + theme(plot.title = element_text(hjust = 0.5)) 

par(family='CM Roman')
nccprob + ccdf
```

# Individuals with High Networked Cultural Capital

```{r}
#Individuals with high or any ncc in Projected DEN
high_ncc <- induced_subgraph(den_mine_ntwk, V(den_mine_ntwk)$ncc > 4)
print(V(high_ncc)$name) #List of individuals with high cultural capital (arbitrary cutoff)

#Names
high_ncc_indivs <- V(high_ncc)$name
```

```{r}
#Print Affiliations for the individuals with ncc of at least 6

#Order individuals by amount of ncc
top_ncc_df <- gender_df[order(-gender_df$ncc),]
top_ncc_df[1:20,]

#Print Cultural Affiliations
for(i in 1:8){
  print(top_ncc_df$name[i])
  affils <- den[den$NAME == top_ncc_df$name[i],]$AFFILIATION
  for (affil in affils){
    if (culture_df[culture_df$den.AFFILIATION == affil,]$cultural_label == 1)
      print(affil)
  }
}
```

```{r}
# #More detail on an individual's cultural affiliations
# for(i in 2:2){
#   affils <- den[den$NAME == top_ncc_df$name[i],]$AFFILIATION
#   for (affil in affils){
#     if (culture_df[culture_df$den.AFFILIATION == affil,]$cultural_label == 1)
#       print(culture_df[culture_df$den.AFFILIATION == affil, c(1, 2, 3, 284, 285, 286, 287, 288)])
#   }
# }
```

# Miscellaneous Data Checks

### Checking how many ncc = 1 and deg = 1 in main network
```{r}
#Names with degree 1
namesdeg1 <- degree_df[degree_df$deg ==1,]$names

#Get length
length(namesdeg1) #29382

#NCC of Vertices with name in namesdeg1
ncc_namesdeg1 <- V(den_mine_largest)[V(den_mine_largest)$name %in% namesdeg1]$ncc

#How many equal 1
table(ncc_namesdeg1) #2424

#Proportion
2424/29382 #0.082
```

### Proportion of Affiliations with a CVR

```{r}
#Proportion of Affiliations with a CVR
length(unique(den$AFFILIATION))
length(unique(den[den$CVR == FALSE,]$AFFILIATION))
2625/5079
```

