---
title: "RQ2: How are other measures of individual status in the network related to cultural capital?"
output: html_document
date: '2022-07-04'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# RQ2: How are other measures of individual status in the network related to cultural capital?
To load network objects required for subsequent analysis into global R environment, run DEN Subgraphs.Rmd

# Load packages 
```{r}
library(igraph)
library(igraphdata)
library(scales)
library(tidyr)
library(forcats)
library(dplyr)


library(stargazer)
library(ggplot2)
library(hrbrthemes)
library(viridis)

library(ergm)
library(pals)
```

# Network measures of importance: Largest Component DEN

## Weighted Eigenvector Centrality
```{r}
#Calculate Centrality Measures

#Weighted Eigenvector Centrality
#evcent: This function interprets weights as connection strength. Higher weights spread the centrality better.
eig <- evcent(den_mine_largest, weights = E(den_mine_largest)$weight)$vector

#Highest weighted eigenvector centralities
eig_sort <- sort(eig, decreasing = TRUE)
head(eig_sort)
```

```{r}
#Negative Binomial Model
eig.nb <- glm.nb(V(den_mine_largest)$ncc ~ eig)
summary(eig.nb)
```


## Betweenness Centrality
```{r}
#Betweenness Centrality
bet <- betweenness(den_mine_largest)

#Highest betweenness centralities
bet_sort <- sort(bet, decreasing = TRUE)
head(bet_sort)
```

```{r}
#Negative Binomial Model
bet.nb <- glm.nb(V(den_mine_largest)$ncc ~ bet)
summary(bet.nb)
```


## Centrality Leaders

```{r}
#top in centrality measures
bet100 <- bet_sort[1:100]
sink("bet100.txt")
bet100
sink()

eig100 <- eig_sort[1:100]
sink("eig100.txt")
eig100
sink()
```

```{r}
#Write to CSV
write.csv(names(eig_sort[1:100]), "eig100.csv")
write.csv(names(bet_sort[1:100]), "bet100.csv")
```

## Network measures of importance: Largest Component DEN (Without Cultural Ties)
Graph without cultural ties (not_cultural_graph)

## Weighted Eigenvector Centrality
```{r}
#evcent: This function interprets weights as connection strength. Higher weights spread the centrality better.
eig_notcult <- evcent(not_cultural_graph, weights = E(not_cultural_graph)$weight)$vector

#Highest weighted eigenvector centralities
eig_sort_notcult <- sort(eig_notcult, decreasing = TRUE)
head(eig_sort_notcult)
```

```{r}
#Negative Binomial Model
eignc.nb <- glm.nb(V(den_mine_largest)$ncc ~ eig_notcult)
summary(eignc.nb)
```

## Betweenness Centrality
```{r}
#Betweenness Centrality
bet_notcult <- betweenness(not_cultural_graph)

#Highest betweenness centralities
bet_sort_notcult <- sort(bet_notcult, decreasing = TRUE)
head(bet_sort_notcult)
```

```{r}
#Negative Binomial Model
betnc.nb <- glm.nb(V(den_mine_largest)$ncc ~ bet_notcult)
summary(betnc.nb)
```

## Outputs

```{r}
#stargazer(eig.nb, eignc.nb)
#stargazer(bet.nb, betnc.nb)
```


## Plots

```{r}
#Base R
plot(log(eig), V(den_mine_largest)$ncc, pch = 20, cex=0.4) #Plot against ncc
plot(log(bet), V(den_mine_largest)$ncc) 
plot(log(eig_notcult), V(not_cultural_graph)$ncc, pch = 20, cex=0.4)
plot(log(bet_notcult), V(not_cultural_graph)$ncc)
```
```{r}
#ggplot
rq2_plotdata <- data.frame(ncc = V(den_mine_largest)$ncc,
                           eig,
                           eig_notcult,
                           bet,
                           bet_notcult)
```


```{r}
#Scatter Plots
set.seed(33200)

ggplot(rq2_plotdata, aes(x = eig, y = ncc)) +
  #scale_x_continuous(trans='log10') +
  geom_jitter(color = "#1B9CFC", alpha = 0.5) +
  labs (x = "Weighted Eigenvector Centrality",
        y = "Networked Cultural Capital") 

ggplot(rq2_plotdata, aes(x = bet, y = ncc)) +
  #scale_x_continuous(trans='log10') +
  geom_jitter(color = "#1B9CFC", alpha = 0.5) +
  labs (x = "Betweenness Centrality",
        y = "Networked Cultural Capital")
```


```{r}
#Violin Plots
#Source: https://r-graph-gallery.com/violin_horizontal_ggplot2.html
rq2_plotdata$ncc <- factor(rq2_plotdata$ncc, levels = c("0", "1", "2", "3", "4", "5", "6", "7", "8"))

p_eig <- rq2_plotdata %>%
  ggplot( aes(x=eig, y=ncc, fill=ncc, color=ncc)) +
    geom_violin(width=1, size=0.2) +
    scale_x_continuous(trans='log10') +
    scale_fill_viridis(discrete=TRUE) +
    scale_color_viridis(discrete=TRUE) +
    theme_minimal() + 
    theme(legend.position="none") +
    xlab("log Weighted Eigenvector Centrality") +
    ylab("Networked Cultural Capital")

p_eig_nc <- rq2_plotdata %>%
  ggplot( aes(x=eig_notcult, y=ncc, fill=ncc, color=ncc)) +
    geom_violin(width=1, size=0.2) +
    scale_x_continuous(trans='log10') +
    scale_fill_viridis(discrete=TRUE) +
    scale_color_viridis(discrete=TRUE) +
    theme_minimal() + 
    theme(legend.position="none") +
    xlab("log Weighted Eigenvector Centrality, Cultural Ties Removed") +
    ylab("Networked Cultural Capital")

p_eig
p_eig_nc
```


# External measures of status: Core DEN

```{r}
#Simple tables
table(V(core_subgraph)$famclass)
table(V(core_subgraph)$famclass, V(core_subgraph)$ncc)

#Proportions table
classtab <- table(V(core_subgraph)$famclass, V(core_subgraph)$ncc)
prop.table(x = classtab, margin = 1)
```


```{r}
#Negative binomial regression by family class
coredatanb <- data.frame(ncc = V(core_subgraph)$ncc, class = V(core_subgraph)$famclass)
coredatanb$class <- as.factor(coredatanb$class)
coredatanb <- within(coredatanb, class <- relevel(class, ref = "Working class"))
glm.nb <- glm.nb(ncc ~ class, data = coredatanb)
summary(glm.nb)

#stargazer(glm.nb)
```

