---
title: "RQ3 ERGMs"
output: html_document
date: '2022-07-02'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# RQ3: How is cultural capital associated with the formation of connections among the Danish elite?
To load network objects required for subsequent analysis into global R environment, run DEN Subgraphs.Rmd

# Load Packages

```{r}
library(igraph)
library(igraphdata)
library(scales)
library(dplyr)

library(stargazer)
library(ggplot2)
library(ergm)
library(pals)
```

# ERGM Graph Prep

## Simplify graphs

```{r}
#Simplify Core DEN
culture_core_sna <- simplify(culture_core)
nonculture_core_sna <- simplify(nonculture_core)
```

```{r}
#Simplify Largest Component DEN
not_cultural_graph_sna <- simplify(not_cultural_graph)
cultural_graph_sna <- simplify(cultural_graph)
```

## Load ERGM Packages
```{r}
require(intergraph)
detach(package:igraph)
require(sna)
require(ergm)
```

## Transform to sna objects

```{r}
#Core DEN
culture_core_sna<-asNetwork(culture_core_sna)
nonculture_core_sna <-asNetwork(nonculture_core_sna)

#Largest Component DEN
not_cultural_graph_sna <- asNetwork(not_cultural_graph_sna)
cultural_graph_sna <- asNetwork(cultural_graph_sna)
```

# Core DEN - With full set of controls
```{r}
ergm_cf <- ergm(nonculture_core_sna ~ edges 
              + nodematch("sector") 
              + nodematch("educat") 
              + nodematch("famclass", diff = TRUE)
              + nodecov("age")
              + absdiff("age")
              + nodematch("uni")
              + nodematch ("gender")
              + nodecov("ncc")
              + edgecov(culture_core_sna))

summary(ergm_cf)
#stargazer(ergm_cf)
```

```{r}
#Diagnostics
goftest <- gof(ergm_cf)
plot(goftest)
```


# Core DEN

```{r}
ergm_cp <- ergm(nonculture_core_sna ~ edges #Preserves density
              + nodematch("gender") #Gender homophily
              + nodecov("ncc")
              + edgecov(culture_core_sna)) #Sharing cultural tie


summary(ergm_cp)
#stargazer(ergm_cp)
```


```{r}
#Diagnostics
goftest <- gof(ergm_cp)
plot(goftest)
```

```{r}

median(degree(core_subgraph))
```


# Largest DEN Component

```{r}
ergm_fp <- ergm(not_cultural_graph_sna ~ edges #Preserves density
              + nodematch("gender") #Gender homophily
              + nodecov("ncc")
              + edgecov(cultural_graph_sna)) #Sharing cultural tie

summary(ergm_fp)
#stargazer(ergm_fp)
```


```{r}
#Diagnostics
mcmc.diagnostics(ergm_fp)
```

## Detach ERGM Packages
```{r}
detach(package:sna)
require(igraph)
```

# Robustness Check - By Sector

## List of affiliations by sector

```{r}
#Affiliations by other sector
sci_affils <- affiliations[affiliations$Science == 1,]$den.AFFILIATION #Science
pol_affils <- affiliations[affiliations$Politics == 1,]$den.AFFILIATION #Politics
fin_affils <- affiliations[affiliations$Finance== 1,]$den.AFFILIATION #Finance
union_affils <- affiliations[affiliations$Unions== 1,]$den.AFFILIATION #Unions

#Check how many per category
length(pol_affils)
length(fin_affils)
length(union_affils)
length(sci_affils)

```

## Run Sector ERGM

```{r}
`%notin%` <- Negate(`%in%`)

  #Remove edges which represent an organization in the list
  selected_edges <- E(core_subgraph)[E(core_subgraph)$affiliation %in% union_affils] #Replace union_affils to get diff sector
  other_edges <- E(core_subgraph)[E(core_subgraph)$affiliation %notin% union_affils]
  
  #Separate graphs
  selected_graph <- core_subgraph - other_edges
  other_graph <- core_subgraph - selected_edges
  
  #Simplify graphs
  selected_graph <- simplify(selected_graph)
  other_graph <- simplify(other_graph)
  
  #Load ERGM Packages
  require(intergraph)
  detach(package:igraph)
  require(sna)
  require(ergm)
  
  #Convert to statnet objects
  selected_graph <- asNetwork(selected_graph)
  other_graph <-asNetwork(other_graph)
  
  #Run ERGM
  bootstrap_ergm <- ergm(other_graph ~ edges 
                + nodematch("sector") 
                + nodematch("educat") 
                + nodematch("famclass", diff = TRUE)
                + nodecov("age")
                + absdiff("age")
                + nodematch("uni")
                + nodematch ("gender")
                + nodecov("ncc")
                + edgecov(selected_graph))
  
  print(summary(bootstrap_ergm))
  
  #Note coefficient on edgecov(selected_graph)
  # coef <- summary(bootstrap_ergm)$coefficients[14,1]
  # ncc <- summary(bootstrap_ergm)$coefficients[13,1]
  # coef_list[i] <- coef
  # ncc_list[i] <- ncc
  
  #Remove statnet
  detach(package:sna)
  require(igraph)
  

```


# Robustness Check - Sampling Based on Distribution

## Cultural Labeling by Affiliation Size
```{r}
#Logistic regression of org size vs cultural label
logistic_size <- glm(formula = culture_labels ~ log(countindivs), family = binomial(), data = out)
summary(logistic_size)

# #Outputs:
# stargazer(logistic_size)
# plot(log(out$countindivs), out$culture_labels)
```
```{r}
# Plot Predicted data and original data points
ggplot(out, aes(x=log(countindivs), y=culture_labels)) + geom_point() +
      stat_smooth(method="glm", color="red",
                method.args = list(family=binomial)) +
      labs(x = "log(Affiliation Size)", y = "Cultural Label")

?stat_smooth
```


## Distribution
```{r}
#Smooth Distribution
hist(E(culture_core)$weight) #Original Histogram
plot(density(E(culture_core)$weight, bw = 0.02)) #Smoothed
ncc_density <- density(E(culture_core)$weight, bw = 0.02) #Save smoothed density

new_ncc <- sample(E(culture_core)$weight, 372, replace=TRUE) + rnorm(372, 0, ncc_density$bw) #Sample to distribution
```

## Sampling Affiliations
```{r}
#Take 100000 Samples of Affiliations

`%notin%` <- Negate(`%in%`)
p_vals <- rep(0,100000)
indices <- vector("list", 100000)

for (i in 1:100000){
  if(i%%1000 == 0){
    print(i)
  }
  #Random Sample of Organizations
  org_indices <- sample.int(5079, 646) #Sample number of cultural organizations from full list
  selected_affils <- unique(den$AFFILIATION)[org_indices] #List of sampled organizations
    
  #Remove edges which represent an organization in the list
  selected_edges <- E(core_subgraph)[E(core_subgraph)$affiliation %in% selected_affils]
  other_edges <- E(core_subgraph)[E(core_subgraph)$affiliation %notin% selected_affils]
    
  #Separate graphs
  selected_graph <- core_subgraph - other_edges
  
  #K-S test of weights, smoothed same amount
  sel_density <- density(E(selected_graph)$weight, bw = 0.02)
  new_sel <- sample(E(selected_graph)$weight, 372, replace=TRUE) + rnorm(372, 0, sel_density$bw)
  
  ks <- ks.test(new_ncc, new_sel)
  p <- ks$p.value
  p_vals[i] <- p
  indices[[i]] <- org_indices
}
```


```{r}
#Sort according to p-values
i1 <- order(p_vals, decreasing = TRUE)
p_vals <- p_vals[i1]
indices <- indices[i1]

#Check P Values at index 10, 100
p_vals[10]
p_vals[100]
```

## Run Bootstrapped ERGM
```{r}
#Vector to be filled with coefficients on edgecov() terms
ncc_list <- rep(NA, 100)
coef_list <- rep(NA, 100)
`%notin%` <- Negate(`%in%`)

#Get ERGM
for(i in 1:100){  
  #Random Sample of Organizations
  dist_indices <- indices[[i]]
  selected_affils <- unique(den$AFFILIATION)[dist_indices] #List of sampled organizations
  
  #Remove edges which represent an organization in the list
  selected_edges <- E(core_subgraph)[E(core_subgraph)$affiliation %in% selected_affils]
  other_edges <- E(core_subgraph)[E(core_subgraph)$affiliation %notin% selected_affils]
  
  #Separate graphs
  selected_graph <- core_subgraph - other_edges
  other_graph <- core_subgraph - selected_edges
  
  #Simplify graphs
  selected_graph <- simplify(selected_graph)
  other_graph <- simplify(other_graph)
  
  #Load ERGM Packages
  require(intergraph)
  detach(package:igraph)
  require(sna)
  require(ergm)
  
  #Convert to statnet objects
  selected_graph <- asNetwork(selected_graph)
  other_graph <-asNetwork(other_graph)
  
  #Run ERGM
  bootstrap_ergm <- ergm(other_graph ~ edges 
                + nodematch("sector") 
                + nodematch("educat") 
                + nodematch("famclass", diff = TRUE)
                + nodecov("age")
                + absdiff("age")
                + nodematch("uni")
                + nodematch ("gender")
                + nodecov("ncc")
                + edgecov(selected_graph))
  
  #Note coefficient on edgecov(selected_graph)
  coef <- summary(bootstrap_ergm)$coefficients[14,1]
  ncc <- summary(bootstrap_ergm)$coefficients[13,1]
  coef_list[i] <- coef
  ncc_list[i] <- ncc
  
  #Remove statnet
  detach(package:sna)
  require(igraph)
  
}
```

```{r}
mean(coef_list)
mean(ncc_list)
```

# Core DEN - Weighted ERGM (Doesn't Run)

```{r}
# #Simplify
# core_culture_simpleweighted <- simplify(culture_core, edge.attr.comb=list(weight="sum"))
# core_culture_simpleweighted <- remove.edge.attribute(core_culture_simpleweighted, "affiliation")
# core_culture_simpleweighted <- remove.edge.attribute(core_culture_simpleweighted, "cultural")
# 
# notculture_core_simpleweighted <- simplify(nonculture_core, edge.attr.comb=list(weight="sum"))
# notculture_core_simpleweighted <- remove.edge.attribute(notculture_core_simpleweighted, "affiliation")
# notculture_core_simpleweighted <- remove.edge.attribute(notculture_core_simpleweighted, "cultural")
# 
# summary(notculture_core_simpleweighted)
# summary(E(notculture_core_simpleweighted)$weight)
```

```{r}
# #Load ERGM Packages
# require(intergraph)
# detach(package:igraph)
# require(sna)
# require(ergm)
#   
# #Convert to statnet objects
# ccsw_sna <- asNetwork(core_culture_simpleweighted)
# nccsw_sna <-asNetwork(notculture_core_simpleweighted)
```

```{r}
# install.packages("ergm.count")
# library(ergm.count)

# #Run Weighted ERGM
# ergm_weighted <- ergm(nccsw_sna ~ edges #Preserves density
#               + nodematch("gender") #Gender homophily
#               + nodecov("ncc")
#               + edgecov(ccsw_sna),
#               response = "weight",
#               reference=~Unif(0,0.9),
#               ergmHint=c())
# 
# detach(package:sna)
# require(igraph)
```

```{r}
# summary(ergm_weighted)
```
